### 2024-08-14 manuscript.tex
More references

\begin{table}
% TODO: Add sampling intervals.
\caption{List of voyages and stations. Start, end and days (UTC; inclusive) indicate the time period when the vessel was south of 40°S. Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is rounded to the nearest integer. CL51/31 indicates CL51 configured to emulate CL31.}
\label{tab:voyages}
\small
\begin{tabular}{llllllr}
Name & Vessel & Ceil. & Region & Start & End & Days\\
\hline
AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124\\
HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149\\
MCQ16-18 & /                             & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710\\
NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
PS77/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2010-12-01 & 2011-02-04 & 65 \\
PS77/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-02-07 & 2011-04-14 & 66 \\
PS79/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-12-06 & 2012-01-02 & 27 \\
PS79/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-01-10 & 2012-03-10 & 61 \\
PS79/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-03-14 & 2012-04-08 & 26 \\
PS81/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-12-02 & 2013-01-18 & 47 \\
PS81/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-01-22 & 2013-03-17 & 55 \\
PS81/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-03-18 & 2013-04-16 & 30 \\
PS81/5   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-04-20 & 2013-05-23 & 33 \\
PS81/6   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-06-10 & 2013-08-12 & 63 \\
PS81/7   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-08-15 & 2013-10-14 & 60 \\
PS81/8   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-11-12 & 2013-12-14 & 31 \\
PS81/9   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-12-21 & 2014-03-02 & 71 \\
PS89     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2014-12-05 & 2015-01-30 & 56 \\
PS96     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2015-12-08 & 2016-02-14 & 68 \\
PS97     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-02-15 & 2016-04-06 & 52 \\
PS103    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-12-18 & 2017-02-02 & 46 \\
PS104    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2017-02-08 & 2017-03-18 & 39 \\
PS111    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-01-21 & 2018-03-14 & 52 \\
PS112    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-03-18 & 2018-05-05 & 49 \\
PS117    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-12-18 & 2019-02-07 & 51 \\
PS118    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2019-02-18 & 2019-04-08 & 50 \\
PS123    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-01-10 & 2021-01-31 & 21 \\
PS124    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-02-03 & 2021-03-30 & 55 \\
TAN1502  & RV \emph{Tangaroa}            & CL51/31 & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
TAN1702  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2017-03-09 & 2017-03-31 & 23 \\
TAN1802  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2018-02-07 & 2018-03-20 & 41 \\
\hline
\textbf{Total} &                         &         &          &            &            & \textbf{2421}\\
\end{tabular}
\normalsize
\end{table}

\begin{figure}
\centerline{
\includegraphics[width=1.06\textwidth]{img/cloud_occurrence_panel.pdf}
}
\caption{Cloud occurrence by height for the 31 voyages and one sub-Antarctic
station (MCQ16-18) in observations (OBS), and simulated by the ALCF from the
ICON model, MERRA‐2 (M2) and ERA5 reanalysis data. The numbers in the legend
indicate the total cloud fraction and the number of days of data.}
\label{fig:cloud-occurrence-panel}
\end{figure}

>>>>

\begin{table}
% TODO: Add sampling intervals.
\caption{List of voyages and stations. Start, end and days (UTC; inclusive) indicate the time period when the vessel was south of 40°S. Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is rounded to the nearest integer. CL51/31 indicates CL51 configured to emulate CL31.}
\label{tab:voyages}
\small
\begin{tabular}{llllllr}
\textbf{Name} & \textbf{Vessel} & \textbf{Ceil.} & \textbf{Region} & \textbf{Start} & \textbf{End} & \textbf{Days}\\
\hline
AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124 \\
HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
MICRE    & [Macquarie Is. station]       & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
PS77/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2010-12-01 & 2011-02-04 & 65 \\
PS77/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-02-07 & 2011-04-14 & 66 \\
PS79/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-12-06 & 2012-01-02 & 27 \\
PS79/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-01-10 & 2012-03-10 & 61 \\
PS79/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-03-14 & 2012-04-08 & 26 \\
PS81/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-12-02 & 2013-01-18 & 47 \\
PS81/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-01-22 & 2013-03-17 & 55 \\
PS81/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-03-18 & 2013-04-16 & 30 \\
PS81/5   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-04-20 & 2013-05-23 & 33 \\
PS81/6   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-06-10 & 2013-08-12 & 63 \\
PS81/7   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-08-15 & 2013-10-14 & 60 \\
PS81/8   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-11-12 & 2013-12-14 & 31 \\
PS81/9   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-12-21 & 2014-03-02 & 71 \\
PS89     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2014-12-05 & 2015-01-30 & 56 \\
PS96     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2015-12-08 & 2016-02-14 & 68 \\
PS97     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-02-15 & 2016-04-06 & 52 \\
PS103    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-12-18 & 2017-02-02 & 46 \\
PS104    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2017-02-08 & 2017-03-18 & 39 \\
PS111    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-01-21 & 2018-03-14 & 52 \\
PS112    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-03-18 & 2018-05-05 & 49 \\
PS117    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-12-18 & 2019-02-07 & 51 \\
PS118    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2019-02-18 & 2019-04-08 & 50 \\
PS123    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-01-10 & 2021-01-31 & 21 \\
PS124    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-02-03 & 2021-03-30 & 55 \\
TAN1502  & RV \emph{Tangaroa}            & CL51/31 & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
TAN1702  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2017-03-09 & 2017-03-31 & 23 \\
TAN1802  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2018-02-07 & 2018-03-20 & 41 \\
\hline
\textbf{Total} &                         &         &          &            &            & \textbf{2421}\\
\end{tabular}
\normalsize
\end{table}

\begin{table}
\caption{List of voyage and station references.}
\label{tab:voyage-references}
\small
\begin{tabular}{lp{14.5cm}}
\textbf{Name} & \textbf{References}\\
\hline
AA15-16  & \cite{klekociuk2020} \\
MARCUS   & \cite{mcfarquhar2016,mcfarquhar2019,zhang2017,keeler2017,walton2017,cromwell2017,mcfarquhar2021} \\
MICRE    & \cite{marchand2015,marchand2020,zhang2016,mcfarquhar2021} \\
PS77/2   & \cite{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
PS77/3   & \cite{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
PS79/2   & \cite{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
PS79/3   & \cite{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
PS79/4   & \cite{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
PS81/2   & \cite{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
PS81/3   & \cite{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
PS81/4   & \cite{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
PS81/5   & \cite{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
PS81/6   & \cite{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
PS81/7   & \cite{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
PS81/8   & \cite{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
PS81/9   & \cite{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
PS89     & \cite{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
PS96     & \cite{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
PS97     & \cite{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
PS103    & \cite{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
PS104    & \cite{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
PS111    & \cite{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
PS112    & \cite{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
PS117    & \cite{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
PS118    & \cite{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
PS123    & \cite{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
PS124    & \cite{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
TAN1802  & \cite{kremser2020,kremser2021} \\
\end{tabular}
\end{table}

\begin{figure}
\centerline{
\includegraphics[width=1.06\textwidth]{img/cloud_occurrence_panel.pdf}
}
\caption{Cloud occurrence by height for the 31 voyages and one sub-Antarctic
station (MICRE) in observations (OBS), and simulated by the ALCF from the
ICON model, MERRA‐2 (M2) and ERA5 reanalysis data. The numbers in the legend
indicate the total cloud fraction and the number of days of data.}
\label{fig:cloud-occurrence-panel}
\end{figure}
